A simplified dynamic bioenergetic model for coral-*Symbiodinium* symbioses and coral bleaching as an alternate stable state

### 2017-01-11 JTB_supp/JTB_supp.Rmd
title and caption Fig S9

plot(NA, xlim=range(input$L), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
points(c(48,48,53,53), c(0.22,0.23,0.22,0.23), pch=c(19,1,19,1), cex=c(0.4,1,0.4,1), col=c("black","black","red","red"), xpd=T)
text(38, 0.225, labels="init. S:H", xpd=T, cex=0.7, srt=90)
text(46, c(0.22,0.23), labels=c("0.1", "0.0001"), xpd=T, pos=2, cex=0.7)
text(50, 0.25, labels=c("Steady state growth"), xpd=T, cex=0.7)
text(c(48,53), 0.24, labels=c("pos.", "neg."), xpd=T, cex=0.7)
apply(res1, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

plot(NA, xlim=range(input$L), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
apply(res2, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

plot(NA, xlim=range(input$L), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
apply(res3, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

plot(NA, xlim=range(input$L), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
apply(res4, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

@@

>>>>

plot(NA, xlim=range(input$L), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
title("DIN=1e-7 mol/L; X=2e-6 mol/L")
points(c(48,48,53,53), c(0.22,0.23,0.22,0.23), pch=c(19,1,19,1), cex=c(0.4,1,0.4,1), col=c("black","black","red","red"), xpd=T)
text(38, 0.225, labels="init. S:H", xpd=T, cex=0.7, srt=90)
text(46, c(0.22,0.23), labels=c("0.1", "0.0001"), xpd=T, pos=2, cex=0.7)
text(50, 0.25, labels=c("Steady state growth"), xpd=T, cex=0.7)
text(c(48,53), 0.24, labels=c("pos.", "neg."), xpd=T, cex=0.7)
apply(res1, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

plot(NA, xlim=range(input$L), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
title("DIN=1e-7 mol/L; X=1e-6 mol/L")
apply(res2, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

plot(NA, xlim=range(input$L), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
title("DIN=1e-6 mol/L; X=2e-6 mol/L")
apply(res3, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

plot(NA, xlim=range(input$L), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
title("DIN=1e-6 mol/L; X=4e-6 mol/L")
apply(res4, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

@@

These figures show steady state S:H biomass ratios in constant environments with varying DIN and food (X) levels, with initial S:H biomass values of either 0.1 or 0.0001. Points are colored according to whether the host exhibits positive (black) or negative (red) growth at steady state.
